Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-25 paper/paper.Rmd
added mention of spacv in python; removed duplicate paragraph

This toolbox, implemented as an open-source R package, builds upon and generalizes several existing toolboxes that have been developed in recent years for more specific settings (see Table \@ref(tab:sptcv-methods)).
The earliest and most comprehensive of these implementations is the \pkg{sperrorest} package [@brenning2012], which provides an extendible framework and includes predefined resampling strategies based on, for example, blocking, grouping and buffering. In contrast, \pkg{blockCV} was developed for block and buffer resampling with a focus on species distribution modelling [@blockCV; @rest2014]. Neither of these have been integrated into established machine-learning frameworks such as \pkg{mlr} or \pkg{caret}, and both lack support of temporal prediction tasks. The \pkg{CAST} package, in contrast, focuses on spatiotemporal prediction tasks in a \pkg{caret} framework [@cast; @meyer2018a]. One limitation of these packages is also that they focus on model assessment, while the proposed implementation within the \pkg{mlr} framework offers a seamless integration into model selection.

@@

Thus, \pkg{mlr3spatiotempcv} implements for the first time a comprehensive state-of-the-art compilation of spatial and spatiotemporal partitioning schemes that is well-integrated into a major machine learning framework in R, the \pkg{mlr3} ecosystem [@mlr3].
This package is furthermore equipped with a variety of two- and three-dimensional diagram types.
Our hope is that implementation will facilitate reproducible geospatial modelling and code-sharing across a broad range of application domains.

>>>>

This toolbox, implemented as an open-source R package, builds upon and generalizes several existing toolboxes that have been developed in recent years for more specific settings (see Table \@ref(tab:sptcv-methods)).
The earliest and most comprehensive of these implementations is the \pkg{sperrorest} package [@brenning2012], which provides an extendible framework and includes predefined resampling strategies based on, for example, blocking, grouping and buffering. 
In contrast, \pkg{blockCV} was developed for block and buffer resampling with a focus on species distribution modelling [@blockCV; @rest2014]. 
Neither of these have been integrated into established machine-learning frameworks such as \pkg{mlr} or \pkg{caret}, and both lack support of temporal prediction tasks. 
The \pkg{CAST} package, in contrast, focuses on spatiotemporal prediction tasks in a \pkg{caret} framework [@cast; @meyer2018a]. 
One limitation of these packages is also that they focus on model assessment, while the proposed implementation within the \pkg{mlr} framework offers a seamless integration into model selection.
It is worth noting that a spatial cross-validation library \pkg{spacv} has also recently been developed for Python 3, which can be used with the \pkg{scikit-learn} machine-learning framework [@pedregosa2011].

@@
